%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%            请在此填写摘要            %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}\small
     When we read this problem at the first time, to associate Dragon with ecology  we came up with an idea, create a model centering energy. \\

    First, as fanatical fans of Game of thrones, we select "Mother of Dragons" as the reference object to estimate the Dragon's profile characteristics. Analogy birds, there is a equation shows relations between weight and wingspan. However, we found that this method is not suitable for two animals that are too much different in body size. Through access to information, we know that this equation don't fit creatures with too long wingspan. So we improve the model, and do test with Quetzalcoatlus. The director of this series said the adult Dragon is as heavy as a Boeing 747. Our model match this statement.\\

Second, in order to know energy consumed of Dragon,under our bold speculation, we set up a series of basic models for our futher study. To start with, we reference metabolism equation of land creature, base on this we correct the model. Besides, The result of the first edition fly process modelis too much bigger than expected. According to aerodynamics, considered the pressure difference between above and below the wings, we introduce a correction factor to account for the difference between the size of the wing disc and the actual tube of air displaced by the bird's wings, then pass verification.Then we build a spray flame process model,we assume a special organ for Dragon,and consider this process as flamethrower.Through calculate, we get the energy cost each spray.Now we get a realistic energy model.\\

Finally, we need to consider the energy model of the ecological system. In our opinion, if we want to emphasize the flow of energy in the ecosystem, we need to simplify the food chain and ecosystem energy structure. Then we gathered informations about climate and vegetation coverage of various regions. As a result, we draw figures about the relationship of weight,area,community. In an intuitive way, we shows that Dragon interact with different climate. It tells us the effection of the different regions with very different climates on growing Dragon etc.This just solved the problem of the interaction between the dragon and the ecological environment.\\\\\\\\

\textbf{Keyword: Energy, Aerodynamics, Ecosystem, Heat transfer, Bioenergy}
\end{abstract}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 如不理解以下部分中各命令的含义，请勿修改！ %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%---------以下生成sheet页----------
% 下面的语句可调整全文行距为标准值的0.6倍，请自行使用
%\renewcommand{\baselinestretch}{0.6}\normalsize
\maketitle  % 生成sheet页
\thispagestyle{empty}   % 不要页眉页脚和页码
\setcounter{page}{-100} % 此命令仅是为了避免页码重复报错，不要在意

%---------以下生成目录----------
\newpage
\tableofcontents
\thispagestyle{empty}   % 不要页眉页脚和页码
\newpage

%---------以下生成正文----------
\setlength\parskip{0.8\baselineskip}  % 调整段间距
\setcounter{page}{1}    % 从正文开始计页码
\pagestyle{fancy}